Malacology: A Programmable Storage System

### 2017-02-23 paper/1_intro.tex
paper: wordsmithing - remove confusing OSD/MDS acronyms - capatilize interface names - spell check and fix colors in figures
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

To illustrate the benefits and challenges of this approach we have designed and
evaluated Malacology, a programmable storage system that facilitates the
construction of new services by re-purposing existing subsystem abstractions of
the storage stack.  We build Malacology in Ceph, a popular open source software
storage stack.  We choose Ceph to demonstrate the concept of programmable
storage because it offers a broad spectrum of existing services, including
distributed locking and caching services provided by \newcommentone{file
system} metadata servers, durability and object interfaces provided by the
backend object store, and propagation of consistent cluster state provided by
the monitoring service (see Figure~\ref{fig:overview}).  Malacology is
expressive enough to provide the functionality necessary for implementing new
services.  \addressesissue{4}

>>>>

To illustrate the benefits and challenges of this approach we have designed and
evaluated Malacology, a programmable storage system that facilitates the
construction of new services by re-purposing existing subsystem abstractions of
the storage stack.  We build Malacology in Ceph, a popular open source software
storage stack.  We choose Ceph to demonstrate the concept of programmable
storage because it offers a broad spectrum of existing services, including
distributed locking and caching services provided by \newcommentone{file
system} metadata servers, durability and object interfaces provided by the
back-end object store, and propagation of consistent cluster state provided by
the monitoring service (see Figure~\ref{fig:overview}).  Malacology is
expressive enough to provide the functionality necessary for implementing new
services.  \addressesissue{4}

### 2017-02-23 paper/2_application_specific_storage_stacks.tex
paper: wordsmithing - remove confusing OSD/MDS acronyms - capatilize interface names - spell check and fix colors in figures
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

To demonstrate a recent trend towards more application-specific storage systems
we examine the state of programmability in Ceph. Something of a storage Swiss
army knife, Ceph simultaneously supports file, block, and object interfaces on
a single cluster~\cite{ceph_contributors_ceph_2010}. Ceph's Reliable Autonomous
Distributed Object Storage (RADOS) system is a cluster of object storage
devices (OSDs) that provide Ceph with data durability and integrity using
replication, erasure-coding, and scrubbing~\cite{weil_rados_2007}. Ceph already
provides some degree of programmability; the OSDs support domain-specific
object interfaces that are implemented by composing existing low-level storage
interfaces that execute atomically. These interfaces are written in C++ and are
statically loaded into the system.

@@

The takeaway from Figure~\ref{fig:obj-int-dev-growth} is that programmers are
already trying to use programmability because their needs, whether they be
related to performance, availability, consistency, convenience, etc., are not
satisfied by the existing default set of interfaces. The popularity of the
custom object interface facility of Ceph could be due to a number of reasons,
such as the default algorithms/tunables of the storage system being
insufficient for the application's performance goals, programmers wanting to
exploit application-specific semantics, and/or programmers knowing how to
manage resources to improve performance. A solution based on
application-specific object interfaces is a way to work around the
traditionally rigid storage APIs because custom object interfaces give
programmers the ability to tell the storage system about their application: if
the application is CPU or IO bound, if it has locality, if its size has the
potential to overload a single node, etc.  Programmers often know what the
problem is and how to solve it, but until the ability to modify object
interfaces, they had no way to express to the storage system how to handle
their data.

>>>>

To demonstrate a recent trend towards more application-specific storage systems
we examine the state of programmability in Ceph. Something of a storage Swiss
army knife, Ceph simultaneously supports file, block, and object interfaces on
a single cluster~\cite{ceph_contributors_ceph_2010}. Ceph's Reliable Autonomous
Distributed Object Storage (RADOS) system is a cluster of object storage
devices that provide Ceph with data durability and integrity using
replication, erasure-coding, and scrubbing~\cite{weil_rados_2007}. Ceph already
provides some degree of programmability; the object storage daemons support domain-specific
object interfaces that are implemented by composing existing low-level storage
interfaces that execute atomically. These interfaces are written in C++ and are
statically loaded into the system.

@@

The takeaway from Figure~\ref{fig:obj-int-dev-growth} is that programmers are
already trying to use programmability because their needs, whether they be
related to performance, availability, consistency, convenience, etc., are not
satisfied by the existing default set of interfaces. The popularity of the
custom object interface facility of Ceph could be due to a number of reasons,
such as the default algorithms/tunables of the storage system being
insufficient for the application's performance goals, programmers wanting to
exploit application-specific semantics, and/or programmers knowing how to
manage resources to improve performance. A solution based on
application-specific object interfaces is a way to work around the
traditionally rigid storage APIs because custom object interfaces give
programmers the ability to tell the storage system about their application: if
the application is CPU or I/O bound, if it has locality, if its size has the
potential to overload a single node, etc.  Programmers often know what the
problem is and how to solve it, but until the ability to modify object
interfaces, they had no way to express to the storage system how to handle
their data.

### 2017-02-23 paper/4_malacology_a_programmable_storage_system.tex
paper: wordsmithing - remove confusing OSD/MDS acronyms - capatilize interface names - spell check and fix colors in figures
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

\begin{table*}
\centering\small
\begin{tabular}{ l | c | l | l | l }
%\multicolumn{4}{c}{\Large \textbf{Common Internal Abstractions}} \\
\multicolumn{4}{c}{} \\
\textbf{Interface}                      &
\textbf{Section}                        &
\textbf{Example in Production Systems}  &
\textbf{Example in Ceph}                &
\textbf{Provided Functionality}            \\ \hline
Service Metadata
  & \S\ref{sec:service-metadata-interface}
  & Zookeeper/Chubby coordination~\cite{hunt_zookeeper_2010,burrows_chubby_2006}
  & cluster state management~\cite{website:ceph-mon}
  & consensus/consistency
  \\
Data I/O
  & \S\ref{sec:data-io-interface}
  & Swift in situ storage/compute~\cite{website:zerocloud}
  & object interface classes~\cite{website:cls-lua}
  & transaction/atomicity
  \\
Shared Resource
  & \S\ref{sec:shared-resource-interface}
  & MPI collective IO, burst
  & POSIX metadata protocols
  & serialization/batching
  \\
File Type
  & \S\ref{sec:file-type-interface}
  & ?????
  & file striping strategy
  & data/metadata access
  \\
Load Balancing
  & \S\ref{sec:load-balancing-interface}
  & VMWare's VM migration~\cite{vmware-drs,gulati:hotcloud2011-cloud-resource-management} 
  & migrate POSIX metadata~\cite{weil:sc2004-dyn-metadata}
  & migration/sampling
  \\
Durability
  & \S\ref{sec:durability}
  & S3/Swift interfaces (RESTful API)
  & object store library~\cite{weil_rados_2007}
  & persistence/safety
  \\
\end{tabular}
\caption{Common internal abstractions. The same ``internal abstractions" common
across large-scale systems because they provide primitives that solve general
distributed systems problems.  Here we list examples of what these internal
abstractions are used for in ``production systems" and in Ceph.  Malacology
provides these internal abstractions as interfaces
\newcomment{(Section~\ref{sec:malacology})} that higher level
\oldcomment{applications} \newcomment{services (Section~\ref{sec:services})}
can use.  \oldcomment{; {\it italicized abstractions} are interfaces discussed
in this paper.}}
\addressesissue{1}
\label{table:examples}
\end{table*}

@@

\newcomment{\\ \noindent\it{\textbf{Existing Ceph Implementation: }}} In the
case of Ceph, a consistent view of cluster state among server daemons and
clients is critical to provide strong consistency guarantees to clients.  Ceph
maintains cluster state information in per-subsystem  data structures called
``maps'' that record membership and status information.  A
Paxos~\cite{lamport_parttime_1998} monitoring service is responsible for
integrating state changes into cluster maps, responding to requests from
out-of-date clients and synchronizing members of the cluster whenever there is
a change in a map so that they all observe the same system state. As a
fundamental building block of many system designs, consensus abstractions such
as Paxos are a common technique for maintaining consistent data versions, and
are a useful system to expose.

@@

\noindent{\it{\textbf{Malacology: }}} Malacology exposes a strongly-consistent
view of time-varying service metadata as a service rather than a hidden
internal component. Malacology provides a generic API for adding arbitrary
values to existing subsystem cluster maps. As a consequence of this,
applications can define simple but useful service-specific logic to the
strongly-consistent interface, such as authorization control (just specific
clients can write new values) or triggering actions based on specific values
(e.g. sanitize values).  The higher-level services we implement in
\S\ref{sec:services} make use of this functionality to register, version and
propagate dynamic code (Lua scripts) for new object interfaces defined in
storage daemons (\S\ref{object-data-interface}) and policies in the load
balancer \S\ref{malacology:mds}.  Using this service guarantees that interface
definitions are not only made durable, but are transparently and consistently
propagated throughout the cluster so that clients are properly synchronized
with the latest interfaces.\\

\noindent\newcomment{{\it{\textbf{Impact: }}} provides core functionality
because it lets daemons come to consensus on system critical state. Bugs in the
internal subsystems or ommitting this from services that need this type of
consistency affects correctness.} \addressesissue{3, 5}

@@

\oldcomment{\noindent 4.2 Object I/O Intefrace}
\subsection{Data I/O Interface}
\label{sec:data-io-interface}
\label{object-data-interface}

@@

\newcomment{\\ \noindent\it{\textbf{Existing Ceph Implementation: }}} An object
interface is a plugin structured similarly to that of an RPC in which a
developer creates a named function within the cluster that clients may invoke.
In the case of Ceph each function is implicitly run within the context of an
object specified when the function is called. Developers of object interfaces
express behavior by creating a composition of native interfaces or other custom
object interfaces, and handle serialization of function input and output.  A
wide range of native interfaces are available to developers such as reading and
writing to a byte stream, controlling object snapshots and clones, and
accessing a sorted key-value database. These native interfaces may be
transactionally composed along with application specific logic to create
semantically rich interfaces. An example would be an interface that atomically
updates a matrix stored in the bytestream and an index of the matrix stored in
the key-value database.\\

\begin{figure}[tbp]
\centering
\includegraphics{figures/implementation.png}
\caption{Malacology allows users to dynamically define
object/\newcommentone{file system} metadata interfaces by extending the object
storage daemon (OSD) and metadata server (MDS) subsystems with an embedded Lua
VM.  It uses the service metadata interface (M) to propagate
interfaces/versions across the cluster \label{fig:implementation}}
\end{figure}

\noindent {\it{\textbf{Malacology: }}} The implementation of Ceph's object
abstraction, although powerful, does not readily support programmability.
Supporting only C/C++ for object interface developers, Ceph requires
distribution of compiled binaries for the correct architecture, adding a large
barrier of entry for developers and system administrators. Second, having no
way to dynamically unload modules, any changes require a full restart of a
storage daemon which may have serious performance impacts due to loss of cached
data. And finally, the security limitations of the framework limit the use of
object interfaces to all but those with administrative level access and deep
technical expertise.

@@

\newcomment{\\ \noindent\it{\textbf{Existing Ceph Implementation: }}} In Ceph,
the locking service implements a capability-based system that expresses what
data and \newcommentone{file system} metadata clients are allowed to access as
well as what state they may cache and modify locally.  While designed for the
file abstraction, indexing, locking, and caching are all common services that
are useful to a broad spectrum of applications.  Distributed applications that
share centralized resources (e.g. a database or directory) face similar
challenges which are often solved using application-specific sharding.

\newcomment{\\ \noindent\it{\textbf{Malacology: }}} While the current policy
for sharing access and voluntarily releasing resources is largely best-effort,
Malacology supports generalized policies between metadata servers and clients
that can be used to implement fairness or priority.

@@

\oldcomment{\noindent File type interface.}
\subsubsection{Malacology: File Type Interface}
\label{sec:file-type-interface}

@@

\newcomment{\\ \noindent {\it{\textbf{Malacology: }}}} We allow new inode types
to be defined such that applications can create domain-specific interfaces to
inodes that may modify locking and capability policies. We will show how this
is used in Section~\ref{sec:seq} when we discuss a distributed shared-log built
on Malacology.

@@

\newcomment{Many large scale storage systems separate file system metadata and
data IO so that the corresponding services can scale independently. Metadata
requests transfer small amounts of data and they happen relatively frequently
so many systems employ separate file system metadata clusters.}

\newcomment{\\ \noindent {\it{\textbf{Existing Ceph Implementation: }}}} Ceph
also addresses the challenge of balancing \newcommentone{file system} metadata
load with a separate metadata cluster. This cluster uses load balancing
policies to migrate directory inodes around the cluster to alleviate overload
at single nodes~\cite{weil:sc2004-dyn-metadata}.  The policies use metrics
based on system state (e.g.  CPU and memory utilization) and statistics
collected by the cluster (e.g. the popularity of an inode). Ceph uses dynamic
subtree partitioning to move variable sized namespace subtrees. These units can
be shipped anywhere (i.e., to any metadata server of any capacity) at any time
for any reason. The original balancer was designed with hard-coded policies and
tunables.\\

\noindent {\it{\textbf{Malacology: }}} the existing load balancing mechanisms
are exposed through an API and programmers can customize the behavior through a
domain specific language. These mechanisms include the ability to migrate,
partition, and measure load. Using the Service Metadata and Durability
interfaces, this Load Balancing interface can safely version balancer policies,
save balancer policies in the back-end object store and centralize
warnings/errors. When combined with the File Type interface, load balancing
policies can express a variety of rules for handling multi-tenant and
workloads.

@@

\noindent{\it{\textbf{Existing Ceph Implementation: }}} Ceph provides storage
by striping and replicating data across RADOS~\cite{weil_rados_2007}, the
reliable distributed object store. RADOS protects data using common techniques
such as erasure coding, replication, and scrubbing.  example, when the number
of placement groups change, the OSDs re-balance and re-shard data in the
background in a process called placement group splitting in which OSDs
communicate directly with each other to cover a new state.  In order to reduce
load on the monitoring service, Ceph OSDs use a gossip protocol to efficiently
propagate changes to cluster maps throughout the system, and autonomously
initiate recovery mechanisms when failures are discovered.\\

\noindent {\it{\textbf{Malacology: }}} Metadata service policies and object
storage interfaces are stored durability within RADOS and managed by storing
references with the object maps. Since the cluster already propagates a
consistent view of these data structures, we use this service to automatically
install interfaces in OSDs, and install policies within the metadata server
daemon (MDS) such that clients and daemons are synchronized on
correct implementations without restarting.

>>>>

\begin{table*}
\centering\small
\begin{tabular}{ l | c | l | l | l }
%\multicolumn{4}{c}{\Large \textbf{Common Internal Abstractions}} \\
\multicolumn{4}{c}{} \\
\textbf{Interface}                      &
\textbf{Section}                        &
\textbf{Example in Production Systems}  &
\textbf{Example in Ceph}                &
\textbf{Provided Functionality}            \\ \hline
Service Metadata
  & \S\ref{sec:service-metadata-interface}
  & Zookeeper/Chubby coordination~\cite{hunt_zookeeper_2010,burrows_chubby_2006}
  & cluster state management~\cite{website:ceph-mon}
  & consensus/consistency
  \\
Data I/O
  & \S\ref{sec:data-io-interface}
  & Swift in situ storage/compute~\cite{website:zerocloud}
  & object interface classes~\cite{website:cls-lua}
  & transaction/atomicity
  \\
Shared Resource
  & \S\ref{sec:shared-resource-interface}
  & MPI collective I/O, burst
  & POSIX metadata protocols
  & serialization/batching
  \\
File Type
  & \S\ref{sec:file-type-interface}
  & ?????
  & file striping strategy
  & data/metadata access
  \\
Load Balancing
  & \S\ref{sec:load-balancing-interface}
  & VMWare's VM migration~\cite{vmware-drs,gulati:hotcloud2011-cloud-resource-management} 
  & migrate POSIX metadata~\cite{weil:sc2004-dyn-metadata}
  & migration/sampling
  \\
Durability
  & \S\ref{sec:durability}
  & S3/Swift interfaces (RESTful API)
  & object store library~\cite{weil_rados_2007}
  & persistence/safety
  \\
\end{tabular}
\caption{Common internal abstractions. The same ``internal abstractions" common
across large-scale systems because they provide primitives that solve general
distributed systems problems.  Here we list examples of what these internal
abstractions are used for in ``production systems" and in Ceph.  Malacology
provides these internal abstractions as interfaces
\newcomment{(Section~\ref{sec:malacology})} that higher level
\oldcomment{applications} \newcomment{services (Section~\ref{sec:services})}
can use.  \oldcomment{; {\it italicized abstractions} are interfaces discussed
in this paper.}}
\addressesissue{1}
\label{table:examples}
\end{table*}

@@

\newcomment{\\ \noindent\it{\textbf{Existing Ceph Implementation: }}} 
a consistent view of cluster state among server daemons and
clients is critical to provide strong consistency guarantees to clients.  Ceph
maintains cluster state information in per-subsystem  data structures called
``maps'' that record membership and status information.  A
Paxos~\cite{lamport_parttime_1998} monitoring service is responsible for
integrating state changes into cluster maps, responding to requests from
out-of-date clients and synchronizing members of the cluster whenever there is
a change in a map so that they all observe the same system state. As a
fundamental building block of many system designs, consensus abstractions such
as Paxos are a common technique for maintaining consistent data versions, and
are a useful system to expose.

@@

\noindent{\it{\textbf{Malacology: }}} we expose a strongly-consistent
view of time-varying service metadata as an interface rather than a hidden
internal component. Malacology provides a generic API for adding arbitrary
values to existing subsystem cluster maps. As a consequence of this,
applications can define simple but useful service-specific logic to the
strongly-consistent interface, such as authorization control (just specific
clients can write new values) or triggering actions based on specific values
(e.g. sanitize values).  The higher-level services we implement in
\S\ref{sec:services} make use of this functionality to register, version and
propagate dynamic code (Lua scripts) for new object interfaces defined in
storage daemons (\S\ref{object-data-interface}) and policies in the load
balancer \S\ref{malacology:mds}.  Using this service guarantees that interface
definitions are not only made durable, but are transparently and consistently
propagated throughout the cluster so that clients are properly synchronized
with the latest interfaces.\\

\noindent\newcomment{{\it{\textbf{Impact: }}} provides core functionality
because it lets daemons come to consensus on system critical state. Bugs in the
internal subsystems or omitting this from services that need this type of
consistency affects correctness.} \addressesissue{3, 5}

@@

\oldcomment{\noindent 4.2 Object I/O Interfrace}
\subsection{Data I/O Interface}
\label{sec:data-io-interface}
\label{object-data-interface}

@@

\newcomment{\\ \noindent\it{\textbf{Existing Ceph Implementation: }}} an object
interface is a plugin structured similarly to that of an RPC in which a
developer creates a named function within the cluster that clients may invoke.
In the case of Ceph each function is implicitly run within the context of an
object specified when the function is called. Developers of object interfaces
express behavior by creating a composition of native interfaces or other custom
object interfaces, and handle serialization of function input and output.  A
wide range of native interfaces are available to developers such as reading and
writing to a byte stream, controlling object snapshots and clones, and
accessing a sorted key-value database. These native interfaces may be
transactionally composed along with application specific logic to create
semantically rich interfaces. An example would be an interface that atomically
updates a matrix stored in the bytestream and an index of the matrix stored in
the key-value database.\\

\begin{figure}[tbp]
\centering
\includegraphics{figures/implementation.png}
\caption{Malacology allows users to dynamically define
object/\newcommentone{file system} metadata interfaces by extending the object
storage daemon (OSD) and metadata server (MDS) subsystems with an embedded Lua
VM.  It uses the Service Metadata interface in the monitor (M) to propagate
interfaces/versions across the cluster \label{fig:implementation}}
\end{figure}

\noindent {\it{\textbf{Malacology: }}} the implementation of Ceph's object
abstraction, although powerful, does not readily support programmability.
Supporting only C/C++ for object interface developers, Ceph requires
distribution of compiled binaries for the correct architecture, adding a large
barrier of entry for developers and system administrators. Second, having no
way to dynamically unload modules, any changes require a full restart of a
storage daemon which may have serious performance impacts due to loss of cached
data. And finally, the security limitations of the framework limit the use of
object interfaces to all but those with administrative level access and deep
technical expertise.

@@

\newcomment{\\ \noindent\it{\textbf{Existing Ceph Implementation: }}}
the locking service implements a capability-based system that expresses what
data and \newcommentone{file system} metadata clients are allowed to access as
well as what state they may cache and modify locally.  While designed for the
file abstraction, indexing, locking, and caching are all common services that
are useful to a broad spectrum of applications.  Distributed applications that
share centralized resources (e.g. a database or directory) face similar
challenges which are often solved using application-specific sharding.

\newcomment{\\ \noindent\it{\textbf{Malacology: }}} while the current policy
for sharing access and voluntarily releasing resources is largely best-effort,
Malacology supports generalized policies between metadata servers and clients
that can be used to implement fairness or priority.

@@

\oldcomment{\noindent File type interface.}
\subsubsection{File Type Interface}
\label{sec:file-type-interface}

@@

\newcomment{\\ \noindent {\it{\textbf{Malacology: }}}} allows new inode types
to be defined such that applications can create domain-specific interfaces to
inodes that may modify locking and capability policies. We will show how this
is used in Section~\ref{sec:seq} when we discuss a distributed shared-log built
on Malacology.

@@

\newcomment{Many large scale storage systems separate file system metadata and
data I/O so that the corresponding services can scale independently. Metadata
requests transfer small amounts of data and they happen relatively frequently
so many systems employ separate file system metadata clusters.}

\newcomment{\\ \noindent {\it{\textbf{Existing Ceph Implementation: }}}} 
addresses the challenge of balancing \newcommentone{file system} metadata
load with a separate metadata cluster. This cluster uses load balancing
policies to migrate directory inodes around the cluster to alleviate overload
at single nodes~\cite{weil:sc2004-dyn-metadata}.  The policies use metrics
based on system state (e.g.  CPU and memory utilization) and statistics
collected by the cluster (e.g. the popularity of an inode). Ceph uses dynamic
subtree partitioning to move variable sized namespace subtrees. These units can
be shipped anywhere (i.e., to any metadata server of any capacity) at any time
for any reason. The original balancer was designed with hard-coded policies and
tunables.\\

\noindent {\it{\textbf{Malacology: }}} the existing load balancing mechanisms
are exposed through an API and programmers can customize the behavior through a
domain specific language. These mechanisms include the ability to migrate,
partition, and measure load. Using the Service Metadata and Durability
interfaces, this Load Balancing interface can safely version balancer policies,
save balancer policies in the back-end object store and centralize
warnings/errors. When combined with the File Type interface, the Load Balancing
interface can express policies for handling a variety of multi-tenant
workloads.

@@

\noindent{\it{\textbf{Existing Ceph Implementation: }}} provides storage
by striping and replicating data across RADOS~\cite{weil_rados_2007}, the
reliable distributed object store. RADOS protects data using common techniques
such as erasure coding, replication, and scrubbing. For example, when the number
of placement groups change, the object storage daemons re-balance and re-shard data in the
background in a process called placement group splitting in which object storage daemons
communicate directly with each other to cover a new state.  In order to reduce
load on the monitoring service, the object storage daemons use a gossip protocol to efficiently
propagate changes to cluster maps throughout the system, and autonomously
initiate recovery mechanisms when failures are discovered.\\

\noindent {\it{\textbf{Malacology: }}} metadata service policies and object
storage interfaces are stored durability within RADOS and managed by storing
references with the object maps. Since the cluster already propagates a
consistent view of these data structures, we use this service to automatically
install interfaces in object storage daemons, and install policies within the metadata server
daemon such that clients and daemons are synchronized on
correct implementations without restarting.

### 2017-02-23 paper/5_services_built_on_malacology.tex
paper: wordsmithing - remove confusing OSD/MDS acronyms - capatilize interface names - spell check and fix colors in figures
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

In this section we describe two services built on top of Malacology. The first
is Mantle~\cite{sevilla:sc15-mantle}, a framework for dynamically specifying metadata load balancing
policies. The second system, ZLog, is a high-performance distributed
shared-log.  In addition to these services, we'll demonstrate how we combine
ZLog and Mantle to implement service-aware metadata load balancing policies.

@@

Mantle~\cite{sevilla:sc15-mantle} is a programmable load balancer that separates the metadata balancing
policies from their mechanisms. Administrators inject code to change how the
metadata cluster distributes metadata. Our previous work showed how 
to use Mantle to implement a single node metadata
service, a distributed metadata service with hashing, and a distributed
metadata service with dynamic subtree partitioning. 
We have re-implmented Mantle on Malacology so that Mantle can enjoy the
properties of existing internal abstractions.

@@

With Malacology, Mantle stores the version of the current load balancer in the
Ceph service metadata interface. The version of the load balancer corresponds
to an object name in the balancing policy. Using the service metadata interface
ensures that all metadata servers use the same version of the load balancer. As
a result, the policy version inherits the consistency of Ceph's internal
monitor daemons. The user changes the version of the load balancer using a new
CLI command.

@@

The load balancer version described above corresponds to the name of an object
in RADOS that holds the actual Lua balancing code.  When MDS nodes start
balancing load, they first check the latest version from the MDS map and
compare it to the balancer they have loaded. If the version has changed, they
dereference the pointer to the balancer version by reading the corresponding
object in RADOS. This is in contrast to the original balancer which stored load
balancer code on the local file system -- a technique which is unreliable and
may result in silent corruption.

The balancer pulls the Lua code from RADOS synchronously; asynchronous reads
are not possible because of the architecture of the MDS. The synchronous
behavior is not the default behavior for RADOS operations, so we achieve this
with a timeout: if the asynchronous read does not come back within half the
balancing tick interval the operation is canceled and a Connection Timeout
error is returned. By default, the balancing tick interval is 10 seconds, so
Mantle will use a 5 second second timeout.

This design allows Mantle to immediately return an error if anything
RADOS-related goes wrong.  We use this implementation because we do not want to
do a blocking OSD read from inside the global MDS lock. Doing so would bring
down the MDS cluster if any of the OSDs are not responsive.

Storing the balancers in RADOS is simplified by the use of an interpreted
language for writing balancer code. If we used a language that needs to be
compiled, like the C++ object classes in the OSD, we would need to ensure
binary compatibility, which is complicated by different operating systems,
distributions, and compilers.

@@

In the original implementation, Mantle would log all errors, warnings, and
debug messages to a log stored locally on each MDS server. To get the simplest
status messages or to debug problems, the user would have to log into each MDS
individually, look at the logs, and reason about causality and ordering.

With Malacology, Mantle re-uses the centralized logging features of the
monitoring service. Important errors, warnings, and info messages are collected
by the monitoring subsystem and appear in the monitor cluster log so instead of
users going to each node, they can watch messages appear at the monitor.
Messages are logged sparingly, so as not to spam the monitor with frivolous
debugging but important events, like balancer version changes or failed
subsystems show up in the centralized log.

@@

High-performance in CORFU is achieved using a sequencer service that assigns
log positions to clients by reading from a volatile, in-memory counter which
can run at a very high throughput and at low latency. Since the sequencer is
centralized, ensuring serializability in the common case is trivial.  The
primary challenge in CORFU is handling the failure of the sequencer in a way
that preserves correctness. Failure of the sequencer service in CORFU is
handled by a recovery algorithm that recomputes the new sequencer state using a
CORFU-specific custom storage interface to discover the tail of the log, while
simultaneously invalidating stale client requests using an epoch-based
protocol.

{\bf Sequencer interface.} The sequencer resource supports the ability to
\emph{read()} the current tail value and get the \emph{next()} position in the
log which also atomically increments the tail position.  We implement the
sequencer service in Malacology as an application-specific file type that
associates a small amount of metadata with the inode state managed by the Ceph
metadata service.  This approach has the added benefit of allowing the metadata
service to handle naming, by representing each sequencer instance in the
standard POSIX hierarchical namespace. The primary challenge in mapping the
sequencer resource to the metadata service is handling serialization correctly
to maintain the global ordering provided by the CORFU protocol.

@@

{\bf Balancing policies.} As opposed to the batching mode for controlling
access to the sequencer resource, more predictable latency can be achieved by
treating the sequencer inode as a shared non-cacheable resource, forcing
clients to make a round-trip to the metadata service. However, the shared
nature of the metadata service may prevent the sequencer from achieving maximum
throughput. To provide a solution to this issue we have taken advantage of the
programmability of the metadata service load balancing to construct a
service-specific load balancing policy. As opposed to a balancing policy that
strives for uniform load distribution, a ZLog-specific policy may utilize
knowledge of inode types to migrate the sequencer service to provisioned
hardware during periods of contention or high demand.

@@

In order to repopulate the sequencer state (i.e. the cached, current tail of
the log) during recovery of a sequencer, the maximum position in the log must
be obtained. To do this, the storage interface exposes an additional
\emph{seal} method that atomically installs a new epoch value and returns the
maximum log position that has been written.

>>>>

In this section we describe two services built on top of Malacology. The first
is Mantle~\cite{sevilla:sc15-mantle}, a framework for dynamically specifying file system metadata load balancing
policies. The second system, ZLog, is a high-performance distributed
shared-log.  In addition to these services, we'll demonstrate how we combine
ZLog and Mantle to implement service-aware metadata load balancing policies.

@@

Mantle~\cite{sevilla:sc15-mantle} is a programmable load balancer that separates the metadata balancing
policies from their mechanisms. Administrators inject code to change how the
metadata cluster distributes metadata. Our previous work showed how 
to use Mantle to implement a single node metadata
service, a distributed metadata service with hashing, and a distributed
metadata service with dynamic subtree partitioning. 
We have re-implemented Mantle on Malacology so that Mantle can enjoy the
properties of existing internal abstractions.

@@

With Malacology, Mantle stores the version of the current load balancer in the
Service Metadata interface. The version of the load balancer corresponds
to an object name in the balancing policy. Using the Service Metadata interface
ensures that all metadata servers use the same version of the load balancer. As
a result, the policy version inherits the consistency of Ceph's internal
monitor daemons. The user changes the version of the load balancer using a new
CLI command.

@@

The load balancer version described above corresponds to the name of an object
in RADOS that holds the actual Lua balancing code.  When metadata server nodes start
balancing load, they first check the latest version from the metadata server map and
compare it to the balancer they have loaded. If the version has changed, they
dereference the pointer to the balancer version by reading the corresponding
object in RADOS. This is in contrast to the original balancer which stored load
balancer code on the local file system -- a technique which is unreliable and
may result in silent corruption.

The balancer pulls the Lua code from RADOS synchronously; asynchronous reads
are not possible because of the architecture of the metadata server. The synchronous
behavior is not the default behavior for RADOS operations, so we achieve this
with a timeout: if the asynchronous read does not come back within half the
balancing tick interval the operation is canceled and a Connection Timeout
error is returned. By default, the balancing tick interval is 10 seconds, so
Mantle will use a 5 second second timeout.

This design allows Mantle to immediately return an error if anything
RADOS-related goes wrong.  We use this implementation because we do not want to
do a blocking object storage daemon read from inside the global metadata server lock. Doing so would bring
down the metadata server cluster if any of the object storage daemons are not responsive.

Storing the balancers in RADOS is simplified by the use of an interpreted
language for writing balancer code. If we used a language that needs to be
compiled, like the C++ object classes in the object storage daemon, we would need to ensure
binary compatibility, which is complicated by different operating systems,
distributions, and compilers.

@@

In the original implementation, Mantle would log all errors, warnings, and
debug messages to a log stored locally on each metadata server. To get the simplest
status messages or to debug problems, the user would have to log into each metadata server
individually, look at the logs, and reason about causality and ordering.

With Malacology, Mantle re-uses the centralized logging features of the
monitoring service. Important errors, warnings, and info messages are collected
by the monitoring subsystem and appear in the monitor cluster log so instead of
users going to each node, they can watch messages appear at the monitor.
Messages are logged sparingly, so as not to overload the monitor with frivolous
debugging but important events, like balancer version changes or failed
subsystems show up in the centralized log.

@@

High-performance in CORFU is achieved using a sequencer service that assigns
log positions to clients by reading from a volatile, in-memory counter which
can run at a very high throughput and at low latency. Since the sequencer is
centralized, ensuring serialization in the common case is trivial.  The
primary challenge in CORFU is handling the failure of the sequencer in a way
that preserves correctness. Failure of the sequencer service in CORFU is
handled by a recovery algorithm that recomputes the new sequencer state using a
CORFU-specific custom storage interface to discover the tail of the log, while
simultaneously invalidating stale client requests using an epoch-based
protocol.

{\bf Sequencer interface.} The sequencer resource supports the ability to
\emph{read()} the current tail value and get the \emph{next()} position in the
log which also atomically increments the tail position.  We implement the
sequencer service in Malacology using the File Type interface.
This approach has the added benefit of allowing the metadata
service to handle naming, by representing each sequencer instance in the
standard POSIX hierarchical namespace. The primary challenge in mapping the
sequencer resource to the metadata service is handling serialization correctly
to maintain the global ordering provided by the CORFU protocol.

@@

{\bf Balancing policies.} As opposed to the batching mode for controlling
access to the sequencer resource, more predictable latency can be achieved by
treating the sequencer inode as a shared non-cacheable resource, forcing
clients to make a round-trip to the metadata service. However, the shared
nature of the metadata service may prevent the sequencer from achieving maximum
throughput. To address this issue we use the Load Balancing interface to construct a
service-specific load balancing policy. As opposed to a balancing policy that
strives for uniform load distribution, a ZLog-specific policy may utilize
knowledge of inode types to migrate the sequencer service to provisioned
hardware during periods of contention or high demand.

@@

In order to repopulate the sequencer state ({\it i.e.} the cached, current tail of
the log) during recovery of a sequencer, the maximum position in the log must
be obtained. To do this, the storage interface exposes an additional
\emph{seal} method that atomically installs a new epoch value and returns the
maximum log position that has been written.
